---
output: rmarkdown::github_document
---

`rosette` : Tools to Work with the [Rosette API](https://developer.rosette.com/api-doc)

You need to put your Rosette API key into your `~/.Renviron` file. For example:

    ROSETTE_API_KEY=someapikeyststring
    
The following functions are implemented:

- `rosette_api_key`:	Get or set ROSETTE_API_KEY value
- `ros_categories`:	Rosette API categorizatioin service
- `ros_embedding`:	Rosette API text embedding service
- `ros_entities`:	Rosette API entity extraction service
- `ros_info`:	Rosette API version info
- `ros_language`:	Rosette API language identification service
- `ros_make_name`:	Make a Name object
- `ros_morph`:	Rosette API morphological analysis service
- `ros_name_similarity`:	Rosette API version info
- `ros_name_translation`:	Rosette API name translation service
- `ros_ping	Rosette`: API availability
- `ros_relationships`:	Rosette API relationship extraction service
- `ros_sentences`:	Rosette API sentence determination service
- `ros_sentiment`:	Rosette API sentiment analysis service
- `ros_tokens`:	Rosette API tokenizatioin service

The following data sets are included:

### Installation

```{r eval=FALSE}
devtools::install_git("https://github.com/hrbrmstr/rosette.git")
```

```{r message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(rosette)

# current verison
packageVersion("rosette")

```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(rosette)
library(testthat)

date()

test_dir("tests/")
```

